Acorn Squash Salad Rounds
  EVOO, 1/2 cup
  Orange Zest, 1.5 tsp
  Acorn Squash, 2.5 lbs
  Maple Spice Blend, 3 tsp
  Salt, 3/4 tsp
  Orange Juice, 1/4 cup
  ACV, 1 tbs
  Mixed Greens, 3 oz
  Feta Cheese, 2 oz
%%%%%%%%%%%%%%%%%

\section{ Acorn Squash Salad Rounds }

4g of sugar in spice blend

\subsection{ Ingredients }

\begin{itemize}
  \item 1/2 cup olive oil, divided
  \item 1 1/2 teaspoons grated orange zest, divided
  \item 1 large acorn squash (2 to 3 pounds)
  \item 3 teaspoons Maple \& Spice Pepper, divided
  \item 3/4 teaspoons kosher salt, divided
  \item 1/4 cup juice from zested orange
  \item 1 tablespoon apple cider vinegar
  \item 2 heaping cups mixed salad greens (about 3 ounces)
  \item 2 ounces feta cheese, crumbled
\end{itemize}

\subsection{ Directions }

\begin{enumerate}
  \item Whisk 1/4 cup of the oil with 1 teaspoon of the orange zest and set aside. Preheat oven to 300 degrees. Cut squash in half horizontally (between the two ends, rather than end-to-end). Scoop out seeds and rinse, removing any pulp so seeds are clean. Lay seeds on a paper towel-lined plate and pat dry. Toss seeds with half of the oil-orange mixture and lay them in a single layer on a parchment-lined baking sheet. Bake for 15 minutes. Remove from oven, transfer to a small bowl and toss with 1 teaspoon of the Maple \& Spice Pepper blend and 1/4 teaspoon of the salt. 

  \item Increase oven temperature to 400 degrees. Carefully slide each squash half into 3/4 to 1-inch rounds to yield 4 total slices. Set slices on the same parchment paper-lined baking sheet used for the seeds. Brush the squash slices with remaining oil-orange mixture. Using 1 teaspoon of the Maple/Pepper/Spice blend, generously sprinkle the slices with seasoning. Bake just until fork tender, 20 to 25 minutes. Sprinkle 1/4 teaspoon of the salt across the slices when they come out of the oven. Transfer to salad plates to cool. 

  \item Prepare dressing by whisking orange juice and vinegar with remaining 1/4 cup oil, 1/2 teaspoon orange zest, 1 teaspoon Maple Spice, and 1/4 teaspoon salt. In a large bowl, toss greens with 1 tablespoon of the dressing. Divide dressed greens evenly atop the squash rounds, nestling greens into the opening. Sprinke with toasted squash seeds and feta. Serve remaining dressing alongside the salad. 
\end{enumerate}
