Recipe
  Soy Sauce, 2 tbs
  Rice Wine Vinegar, 2 tbs
  Sesame Oil, 1.5 tbs
  Light Brown Sugar, 2 tsp
  Boneless Chicken Thighs, 0.75 lbs
  Ginger, 2 tbs
  Garlic, 2 cloves
  Peanut Oil, 3 tbs
  Bok Choy, 0.5 lbs
  Leeks, 0.5 lbs
  Chile Flakes, 0.25 tsp
  Salt, 0.5 tsp
%%%%%%%%%%%%%%%%%

\section{ }

\subsection{ Ingredients }

\begin{itemize}
  \item 2 tablespoons soy sauce
  \item 2 tablespoons rice wine vinegar
  \item 1 ½ tablespoons sesame oil
  \item 2 teaspoons light brown sugar
  \item ¾ pound boneless chicken thighs, cut into 1/2-inch strips
  \item 2 tablespoons finely chopped gingerroot
  \item 2 cloves garlic, finely chopped
  \item 3 tablespoons peanut or vegetable oil
  \item ½ pound bok choy (1 head), trimmed and thinly sliced
  \item 2 leeks (1/2 pound), halved lengthwise and thinly sliced
  \item Pinch chile flakes
  \item Salt, as needed

\end{itemize}

\subsection{ Directions }

\begin{enumerate}

  \item In a medium bowl, whisk together soy sauce, vinegar, sesame oil, and sugar. Pour half the mixture over the chicken, along with half the ginger and half the garlic. Let stand 20 minutes.

  \item Heat a large, 12-inch skillet over high heat until extremely hot, about 5 minutes. Add 1 tablespoon peanut oil and the chicken. Cook, stirring constantly, until meat is cooked through, about 3 minutes. Transfer to a plate.

  \item Add the remaining peanut oil to the skillet. Add the bok choy and cook 1 minute. Stir in the leeks and chili flakes; cook, tossing frequently until bok choy and leeks are tender, about 1 minute. Stir in the marinade and a pinch of salt. Move vegetable mixture to the border of the pan. Add remaining ginger and garlic to center of pan and cook, mashing lightly, until fragrant, about 30 seconds. Return chicken to skillet and combine with ginger, garlic, and vegetables. Can serve immediately. 

\end{enumerate}

\textit{ from NYT Cooking }
