Chicken Lettuce Wraps
  Soy Sauce, 1/3 cup
  Fish Sauce, 1/3 cup
  Mirin, 3 tbs
  Honey, 3 tbs
  Chicken Thighs, 1.5 lbs
  Maifun Rice Noodles, 4 oz
  Bibb Lettuce, 400 g
  Mango, 175 g
  Cucumber Small, 4 oz
  Scallions, 20 g
  Peanuts, 0.5 cups
%%%%%%%%%%%%%%%%%
\section{ Chicken Lettuce Wraps }

\subsection{ Ingredients }

\begin{itemize}
  \item 1/3 cup soy sauce
  \item 1/3 cup fish sauce
  \item 3 tbs mirin
  \item 3 tbs honey
  \item Caribbean style seasoning
  \item 1 1/2 pounds boneless, skinless chicken thighs or breasts
  \item 4 ounces very thin rice sticks (Maifun rice noodles)
  \item 1 head Bibb (or Boston) lettuce, whole leaves plucked, rinsed, and dried
  \item 1 mango, peeled, pitted, and diced
  \item 1/2 cucumber, quartered lengthwise and thinly sliced
  \item 4 scallions, white and green parts sliced
  \item 1/2 cup chopped peanuts (optional)
\end{itemize}

\subsection{ Directions }

  \textit{For the sauce:} Whisk together soy sauce, fish sauce, mirin, honey, and Caribbean style seasoning until the honey is incorporated. Marinate the chicken in half of the sauce, and reserve the other half. 

  \textit{For the chicken:} Pan sear, Grill, or used leftovers.

  \textit{For the garnishes and to serve:} Place noodles in a medium saucepan or heatproof bowl and cover with boiling water. Steep for 10 minutes or until noodles are soft. Drain, rinse with cold water, transfer to a serving bowl and toss with 1 to 2 tablespoons of the reserved sauce. Stack lettuce leaves on a serving plate. Place remaining reserved sauce, mango, cucumber, scallions, and peanuts in separate serving bowls. Serve family-style with extra sauce!

\textit{Spice to Plate}
