\section{Chicken Quinoa Bowls with Balsamic Dressing}

\subsection{ Ingredients }

\begin{itemize}
  \item <1/4 cup> Balsamic Vinegar
  \item <2/3 cup> Water
  \item <1/3 cup> Quinoa, rinsed
  \item <12 oz> Chicken Breast, boneless and skinless halves
  \item <3 tsp> EVOO, divided
  \item <1/4 tsp> Garlic Powder
  \item <1/2 tsp> Salt, divided
  \item <1/4 tsp> Black Pepper, divided
  \item <1/2 lb> Asparagus, fresh, trimmed
  \item <1/4 cup> Greek Yogurt
  \item <1/2 tsp> Spicy Brown Mustard
  \item <1/2> Avocado, ripe, peeled and sliced
  \item <6> Cherry Tomato, halved
\end{itemize}

\subsection{ Directions }

\begin{enumerate}
  \item Place vinegar in a small saucepan; bring to a boil. Cook until slightly thickened, 2-3 minutes. Transfer to a bowl; cool completely.
  \item In a small saucepan, bring water to a boil. Add quinoa. Reduce heat; simmer, covered, until liquid is absorbed, 10-12 minutes. Keep warm.
  \item Preheat broiler. Toss chicken with 2 teaspoons oil, garlic powder, 1/4 teaspoon salt and 1/8 teaspoon pepper. Place on 1 half of a 15x10x1-in. pan coated with cooking spray. Broil 4 in. from heat for 5 minutes. Meanwhile, toss asparagus with the remaining oil, salt and pepper.
  \item Remove pan from oven; turn chicken over. Add asparagus. Broil until a thermometer inserted in chicken reads 165° and asparagus is tender, 3-5 minutes. Let chicken stand 5 minutes before slicing.
  \item For dressing, stir yogurt and mustard into balsamic reduction. To serve, spoon quinoa into bowls; top with chicken, asparagus, avocado and tomatoes. Serve with dressing.
\end{enumerate}
