\section{Classic Chickpea Hummus}

\subsection{ Ingredients }

\begin{itemize}
  \item <15 oz> Chickpeas, cooked
  \item <3.5 tbs> Lemon Juice, about one large lemon
  \item <1 clove> Garlic
  \item <1/2 cup> Tahini, well mixed
  \item <3/4 tsp> Salt, kosher
  \item <1/4 tsp> Black Pepper
  \item <1/4 tsp> Ground Cumin
  \item <3.5 tbs> EVOO, 1/2 tablespoon for drizzling
  \item <1 tsp> Zaatar, and/or sesame seeds (for serving)
\end{itemize}

\subsection{ Directions }

This recipe is obviously made for canned chickpeas, but to maximize nutrition and flavor, consider cooking your own chickpeas. Can be frozen in 15 oz quantities. 

\begin{enumerate}
  \item Start by prepping all of your ingredients: Drain 15½ oz. chickpeas in a strainer or colander and rinse thoroughly. Let drain again while you do the other prep.
  \item Cut 1 lemon in half, remove any visible seeds, and squeeze juice into a small bowl. You should have 3–4 Tbsp.
  \item Smash 1 garlic clove with the flat side of your knife on a cutting board and remove peel. Continue to mash with side of knife until a paste forms. (You can also grate garlic on a microplane if you have one—you're just looking for a fine paste.)
  \item Combine drained chickpeas, 3 Tbsp. lemon juice, garlic, ½ cup tahini, ¾ tsp. salt, 10 cracks pepper, ¼ tsp. cumin, and 2 Tbsp. water in a food processor.
  \item Process until smooth, about 1 minute.
  \item With the motor running, stream in 3 Tbsp. oil, then continue to process until hummus is very light and creamy, about 1 minute longer. Taste and season with more salt, if needed.
  \item Transfer hummus to a shallow bowl, top with za’atar and/or sesame seeds, and drizzle with more oil.
\end{enumerate}
