\section{Roasted Cauliflower and Red Pepper Soup}

\subsection{ Ingredients }

\begin{itemize}
  \item <4.5 oz> Bell Pepper, 2 medium peppers, halved and seeded
  \item <19 oz> Cauliflower, 1 large head, broken into florets (about 7 cups)
  \item <4 tbs> EVOO, divided
  \item <1 cup> Vidalia Onion, chopped
  \item <2 cloves> Garlic, minced
  \item <2.5 tsp> Rosemary, minced
  \item <1/2 tsp> Paprika
  \item <1/4 cup> All-Purpose Flour
  \item <4 cups> Chicken Stock
  \item <1 cup> Milk
  \item <1/2 tsp> Salt
  \item <1/4 tsp> Black Pepper
  \item <1/4 tsp> Ground Cayenne
  \item <5 g> Parmesan Cheese, shredded, optional
\end{itemize}

\subsection{ Directions }

\begin{enumerate}
  \item Preheat broiler. Place peppers on a foil-lined baking sheet, skin side up. Broil 4 in. from heat until skins are blistered, about 5 minutes. Transfer to a bowl; let stand, covered, 20 minutes. Change oven setting to bake; preheat oven to 400°.
  \item Toss cauliflower with 2 tablespoons oil; spread in a 15x10x1-in. pan. Roast until tender, 25-30 minutes, stirring occasionally. Remove skin and seeds from peppers; chop peppers.
  \item In a 6-qt. stockpot, heat remaining 2 Tbsp. oil over medium heat. Add onion; cook until golden and softened, 6-8 minutes, stirring occasionally. Add garlic, rosemary and paprika; cook and stir 1 minute. Stir in flour until blended; cook and stir 1 minute. Gradually stir in stock. Bring to a boil, stirring constantly; cook and stir until thickened.
  \item Stir in cauliflower and peppers. Puree soup using an immersion blender. Or, cool slightly and puree soup in batches in a blender; return to pot. Stir in milk and remaining seasonings; heat through. If desired, serve with Parmesan.
  \item Freeze option: Freeze cooled soup in freezer containers. To use, partially thaw in refrigerator overnight. Heat through in a saucepan, stirring occasionally; add a little stock or milk if necessary.
\end{enumerate}
