Peppercorn & Cheese Crusted Steak
  Filet Mignon, 20 oz
  Peppercorns, 2 tbs
  Salt, 0.5 tsp
  Butter, 0.25 cup
  Panko Bread Crumbs, 0.25 cup
  Dried Basil, 0.5 tsp
  Parmesan Cheese, 2 tbs
  Scallions, 1 oz
  Avocado Oil, 1 tbs
%%%%%%%%%%%%%%%%%

\section{ Peppercorn \& Cheese Crusted Steak }

\subsection{ Ingredients }

\begin{itemize}
  \item 4 filet mignon or tri-tip steaks
  \item 2 tablespoons whole peppercorns, coursely ground
  \item 1/2 tsp kosher salt
  \item 1/4 cup unsalted butter, softened
  \item 1/4 cup Panko bread crumbs
  \item 1/2 tsp dried basil
  \item 2 tbs of Parmesan cheese
  \item 2 scallions, white and green parts minced
  \item 1 tablespoon of Avocado Oil, Ghee, or another oil. 
\end{itemize}

\subsection{ Directions }

\textit{For the steak:} Coat steak in roughly cracked peppercorns and salt. Refrigerate for at least 30 minutes. 

\textit{For the topping:} Thoroughly combine butter, basil, bread crumbs, scallions, and Parmesan. Add salt and pepper to taste. On a sheet of parchment paper, shape scoops of the mixture into four 1/4-inch thick flattened disks that will fit over the entire top of each steak. Leave topping disks on the paper, and refrigerate for at least 30 minutes. 

\textit{To cook:} Preheat broiler and remove the steaks and topping from the refrigerator. Heat oil in a cast iron skillet over high heat. Reduce heat to med-high and add steaks. For a medium-rare to medium steak, sear for 5 to 6 minutes on one side, then flip and cook another 2 to 3 minutes. Working quickly, place a disk of topping on each steak and put the skillet under the broiler until topping is nicely browned with some green still showing, about 3 minutes. Immediately transfer steaks to a platter and let rest for 5 to 10 minutes before serving. 

\textit{"Spice To Plate" Cookbook}
