Swedish Meat Balls
  Sourdough Bread, 36/11 oz
  Milk, 1/4 cup
  Ghee, 3 tbs
  White Onion, 0.5 cups
  Salt, 1.2 tsp
  Chuck, 3/4 lb
  Pork, 3/4 lb
  Egg Yolks, 2 yolks
  Black Pepper, 1/2 tsp
  Allspice, 1/4 tsp
  Nutmeg, 1/4 tsp
  Wheat Flour, 0.25 cups
  Beef Broth, 3 cups
  Heavy Cream, 0.25 cups
%%%%%%%%%%%%%%%%%

\section{ Swedish Meat Balls }
\textit{ Alton Brown's Version }

\subsection{ Ingredients }

\begin{itemize}
  \item 2 slices fresh bread
  \item 1/4 cup milk
  \item 3 tablespoons clarified butter, divided
  \item 1/2 cup finely chopped onion
  \item A pinch plus 1 teaspoon kosher salt
  \item 3/4 pound ground chuck
  \item 3/4 pound ground pork
  \item 2 large egg yolks
  \item 1/2 teaspoon black pepper
  \item 1/4 teaspoon ground allspice
  \item 1/4 teaspoon freshly grated nutmeg
  \item 1/4 cup all-purpose flour
  \item 3 cups beef broth
  \item 1/4 cup heavy cream

\end{itemize}

\subsection{ Directions }

\begin{enumerate}
    \item Preheat oven to 200 degrees F.
    \item Tear the bread into pieces and place in a small mixing bowl along with the milk. Set aside.
    \item In a 12-inch straight sided saute pan over medium heat, melt 1 tablespoon of the butter. Add the onion and a pinch of salt and sweat until the onions are soft. Remove from the heat and set aside.
    \item In the bowl of a stand mixer, combine the bread and milk mixture, ground chuck, pork, egg yolks, 1 teaspoon of kosher salt, black pepper, allspice, nutmeg, and onions. Beat on medium speed for 1 to 2 minutes.
    \item Using a scale, weigh meatballs into 1-ounce portions and place on a sheet pan. Using your hands, shape the meatballs into rounds.
    \item Heat the remaining butter in the saute pan over medium-low heat, or in an electric skillet set to 250 degrees F. Add the meatballs and saute until golden brown on all sides, about 7 to 10 minutes. Remove the meatballs to an ovenproof dish using a slotted spoon and place in the warmed oven.
    \item Once all of the meatballs are cooked, decrease the heat to low and add the flour to the pan or skillet. Whisk until lightly browned, approximately 1 to 2 minutes. Gradually add the beef stock and whisk until sauce begins to thicken. Add the cream and continue to cook until the gravy reaches the desired consistency. Remove the meatballs from the oven, cover with the gravy and serve.


\end{enumerate}
